---
title: "DataScience_Lab5(data.table)"
author: "Sanghyeob Ko"
date: "7/19/2022"
output: pdf_document
---

```{r, message =FALSE, warning =FALSE, error =FALSE}
library(tidyverse)
library(dplyr)
library(data.table)
```


1) Use and show data.table code to select the variables year, month, day, and hour from the imported flights data
```{r}
flights <- fread("nycdata.csv")
flights[, .(year, month, day, hour)]
```


2) Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA
```{r}
flights[carrier == 'DL' & origin == "JFK" & dest == "SEA"]
```


3) Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.
```{r}
flights[carrier == 'UA' & month == "3" & air_time < 330]
```


4) Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.  
```{r}
flights %>% 
  # select(carrier, month, air_time) %>% 
  filter(carrier == 'UA', month == '3', air_time < 330) -> f2
f2
```


5) Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour. 
```{r}
flights[, ('avg_airspeed') := .(distance / hour)]
flights
```


6) Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.
```{r}
(flights %>%
  mutate(avg_airspeed = distance / hour) -> flights2)
```


7)
Show and use coding to change the carrier abbreviation of UA to UniitedAir,
7a) data.table method
```{r}
flights[carrier == 'UA', carrier := 'UnitedAir']
flights
```

7b tidyverse method  (Use a sequence of dplyr commands so that you can see the change in your table)
```{r}
flights %>%
  mutate(carrier = recode(carrier, "UA" = "UnitedAir")) -> flights3
flights3
```